Computer Science House Constitution

### 2020-01-17 constitution.tex

The member must also pay dues.

@@

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.

>>>>

The member is not required to pay dues during the Introductory Process.

@@

\asection{Executive Board Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a Selection, the Chairperson may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
